---
title: "Weight of Fish"
author: "Caitlyn Hense"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch

```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight~ .,      
                         data = Perch,
                         nbest = 1,
                         nvmax = NULL,
                         force.in = NULL, force.out = NULL,
                         method = "exhaustive")

summary.out <-summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

This shows that Height and Width is the best model. We can further test the best models.

```{r}
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main="adjr2")
```

### Best Models

The best model is the two element model, H and W models. 

### Best Two regressor model

The best two egressive model is also H and W 

## Pike

```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight~ .,      
                         data = Pike,
                         nbest = 1,
                         nvmax = NULL,
                         force.in = NULL, force.out = NULL,
                         method = "exhaustive")

summary.out <-summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

```{r}
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom", main= "adjr2")
```

### Best Models

The best model is model5 corresponding to L-1,L-2,L-3,H-W

### Best Two regressor model

The best two regressor model are model2; L-1,L-3

Best model is different from best two mdel so we will run ANOVA

```{r}
model5=lm(Weight~ . ,data=Pike)
summary.lm(model5)
model2=lm(Weight~ . -Length2,Height,Width , data=Pike)
anova(model5,model2)
```
##Roach

```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight~ .,      
                         data = Roach,
                         nbest = 1,
                         nvmax = NULL,
                         force.in = NULL, force.out = NULL,
                         method = "exhaustive")

summary.out <-summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

```{r}
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main="adjr2")
```

### Best Models

It seems the best model is model 2 where we can find L3 and W.

### Best Two regressor model

Best two regressor model are both the same, being model2= L3-W

## Final Summary Statements


